What Can Stack Traces Tell us about the Use of Exceptions in Java?

### 2014-05-07 android-stacks.tex
fixing table IX
small changes on paragraph

To answer this question we analyzed general characteristics of stack traces
reported on Java repositories (e.g., exceptions being thrown presented in
Tables~\ref{tab:toptenjava} and ~\ref{tab:toptenandroid}), and took a deeper
look at the stack traces of the Android repositories combining them with with
source code and byte code analyses. Doing so, we mined some characteristics of
stacks that points to best practices violations.

@@

From Tables~\ref{tab:toptenjava}, ~\ref{tab:toptenandroid} we can observe that,
in both Java and Android related issues, direct instances
java.lang.RuntimeException were thrown  (in 10,94\% of Java repositories and
18,88\% of Android repositories respectively). Moreover, after inspecting the
top 100 most thrown exceptions (see ~\ref{tophundrend}) we could observe that
stack traces on which direct instances of java.lang.Exception and
java.lang.Error were thrown. Throwing general exceptions is usually considered a
bad practice, because the type does not carry enough information to identify the
cause of the exceptional behaviour. In such cases, developers need to relying on
exception message which can be neither complete nor precise
~\cite{gosling2000java}.

@@

\begin{table}
\centering
\begin{tabular}{lcccccc}
    \hline
    \bfseries{Type} & \bfseries{Android} & \bfseries{Lib} & \bfseries{Libcore} & \bfseries{Java} & \bfseries{App} & \bfseries{All}\\
    \hline

>>>>

To answer this question we analyzed general characteristics of reported stack traces and, in the case of stack traces reported on Android repositories, we combine stack trace information with
source code and byte code analyses to enable a more detailed analysis.
Doing so, we mined some characteristics of stacks that points to best practices violations.

@@

From Tables~\ref{tab:toptenjava} and ~\ref{tab:toptenandroid} we can observe that,
in both Java and Android related issues, direct instances
java.lang.RuntimeException were thrown  in 10,94\% of Java repositories and
18,88\% of Android repositories respectively. Moreover, after inspecting the
top 100 most thrown exceptions (see ~\ref{tophundrend}) we could observe that
stack traces on which direct instances of java.lang.Exception and
java.lang.Error were thrown.

Throwing general exceptions is usually considered a
bad practice, because the type does not carry enough information to identify the
cause of the exceptional behaviour. In such cases, developers need to relying on
exception message which can be neither complete nor precise
~\cite{gosling2000java}.

@@

\begin{table}
\centering
\begin{tabular}{lcccccc}
    \hline
    \bfseries{Type} & \bfseries{Android} & \bfseries{Libcore} & \bfseries{App} & \bfseries{Lib} & \bfseries{Java} & \bfseries{All}\\
    \hline
